---
title: "Moth"
author: "Murilo Miranda"
date: "9 Sep 2014"
output: html_document
---

## Load Data and Codes
* Read dataset with id, site, period, species, abund

```{r}
data <- read.csv("data.csv", h = T)
head(data)

source('chao.R')
source('distanc.R')
```

---

## Distances
The distances between pairs were calculated using QGIS for IPCC and IGeoE:

* Hayford Gauss IPCC: 
```{r}
dist <- read.csv("dist_mat_ipcc.csv", h = T)
dist <- dist[-1]
DIST1 <- distanc(dist)
head(DIST1)
```

* Hayford Gauss IGeoE
```{r}
dist <- read.csv("dist_mat_igeoe.csv", h = T)
dist <- dist[-1]
DIST2 <- distanc(dist)
head(DIST2)
```

```{r}
par(mfrow=c(2, 1))
hist(DIST1[, 3], main = "IPCC", xlab = "Geographic distance (m)", ylab = "Frequency")
hist(DIST2[, 3], main = "IGEOE", xlab = "Geographic distance (m)", ylab = "Frequency")
```

The histograms have the same behavior, then I chose the first vector of distances (IPCC) for analysing the data.

## Data
Sorensen and Jaccard Estimators were estimated using unseen species (Chao et al 2005). The data-set was subseted by sample. Variables created from the chao-function have the following columns:
```{r}
sample1 <- chao(1, 1, "sample1")
sample2 <- chao(2, 2, "sample2")
sample3 <- chao(3, 3, "sample3")
sample4 <- chao(4, 4, "sample4")
sample5 <- chao(5, 5, "sample5")
sample6 <- chao(6, 6, "sample6")
```

 - p: sampling period.
 - s1: the code of sample 1. 
 - s2: the code of sample 2.
 - n: the number of observed species in the sample 1.
 - nsp1: the number of species in the sample 1.
 - m: the number of observed species in the sample 2.
 - nsp2: the number of species in the sample 2.
 - nsh: the number of observed shared species in the two samples.
 - fm1: the observed number of shared species that occur once in sample 2.
 - fm2: the observed number of shared species that occur twice in sample 2.
 - f1m: the observed number of shared species that occur once in sample 1.
 - f2m: the observed number of shared species that occur twice in sample 1.
 - u_pt1: abundance sum of shared species divided by species number for the sample 1.
 - v_pt1: abundance sum of shared species divided by species number for the sample 2.
 - Junad: Jaccard unadjusted estimator.
 - Lunad: Sorensen unadjusted estimator.
 - U: u_pt1 plus unseen species for the sample 2.
 - V: v_pt1 plus unseen species for the sample 1.
 - Jabd: Jaccard adjusted estimator.
 - Labd: Sorensen adjusted estimator.

```{r}
head(sample1)
```

---

## Exploratory Analysis
These functions were used to synthesize the samples for each year. Moth samplings were conducted for two years (2011 and 2012), each year had three sampling period.

```{r}
trisamples <- function(base1, base2, base3, vr){
  base <- matrix(0, nrow = dim(base1)[1])
  for(i in 1:dim(base1)[1]){
    base[i] <- (base1[i, vr] + base2[i, vr] + base3[i, vr])/3
  }
  base
}

bisamples <- function(base1, base2){
  base <- matrix(0, nrow = length(base1))
  for(i in 1:length(base1)){
    base[i] <- (base1[i] + base2[i])/2
  }
  base
}
```

* Calculated the dissimilarity average per site for first year
```{r}
Jperiod1 <- trisamples(sample1, sample2, sample3, 19)
Lperiod1 <- trisamples(sample1, sample2, sample3, 20)
```

```{r, fig.width = 10}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod1), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod1), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Sorensen")
```

* Calculated the dissimilarity average per site for second year
```{r}
Jperiod2 <- trisamples(sample4, sample5, sample6, 19)
Lperiod2 <- trisamples(sample4, sample5, sample6, 20)
```

```{r, fig.width = 10}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod2), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod2), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Sorensen")
```
* Calculated the dissimilarity average per site for both years
```{r}
Jperiod <- bisamples(Jperiod1, Jperiod2)
Lperiod <- bisamples(Lperiod1, Lperiod2)
```

```{r, fig.width = 10}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Sorensen")
```

**DATASET**: I created a new database with six columns:

  - p: no functionality, I created just to standardize with other functions previously created. 
  - s1: site 1
  - s2: site 2
  - Jabd: Jaccard adjusted estimator
  - Labd: Sorensen adjusted estimator
  - ipcc: distance between site 1 and site 2 (Hayford Gauss IPCC)

```{r}
b.div.mean <- cbind(sample1[, 1], sample1[, 2], sample1[, 3], Jperiod, Lperiod, DIST1[, 3])
colnames(b.div.mean) <- c("p", "s1", "s2", "Jabd", "Labd", "ipcc")

head(b.div.mean)
```

Samples were taken in three landscapes that represent the farmland abandonment gradient: meadow-dominated, shrub-dominated and forest-dominated. In each landscape had 28 fixed sampling sites divided into four biotopes (meadow, short shrub, tall shrub and woodland), totaling 84 sampling sites.

* forest-dominated:
```{r}
mf <- c(56) #m - meadow
sf <- c(36, 39, 42, 45, 46) #s - short shrub
tf <- c(34, 49) #t - tall shrub
wf <- c(29, 30, 31, 32, 33, 35, 37, 38, 40, 41, 43, 44, 47, 48, 50, 51, 52, 53, 54, 55) #w - woodland
```
* shrub-dominated (m - mixed)
```{r}
mm <- c(68, 75, 77, 84)
sm <- c(60, 64, 65, 66, 67, 70, 78, 79, 82)
tm <- c(57, 58, 59, 61, 62, 63, 69, 71, 72, 74, 76)
wm <- c(73, 80, 81, 83)
```
* meadow-dominated (a - agriculture)
```{r}
ma <- c(1, 9, 14, 15, 16, 17, 18, 19, 21, 23, 24, 25, 27)
sa <- c(2, 8, 10, 11, 12, 13, 20)
ta <- c(3, 4, 5, 6, 7, 28)
wa <- c(22, 26)
```

**within landscapes**
```{r}
landsc_within <- function(base, s1, s2){
  result <- NULL
  for(i in s1){
    for(j in s2){
      if(i != j){
        result <- rbind(result, base[base[, 2] == i & base[, 3] == j, ])
      }
    }
  }
  result
}
```

This function creates a database for each landscape. Also, I analyzed separately short and tall shrub within the shrub-dominated landscape.


In this analysis only the biotopes that correspond the type of the landscape were considered.
```{r}
agr.mea <- landsc_within(b.div.mean, ma, ma)
shr.shr <- landsc_within(b.div.mean, sm, sm)
tal.shr <- landsc_within(b.div.mean, tm, tm)
for.woo <- landsc_within(b.div.mean, wf, wf)
mix.shr <- landsc_within(b.div.mean, c(sm, tm), c(sm, tm))
```

**Regression models**

- Jaccard Estimator
```{r}
jmodelfor.woo <- lm((1 - for.woo[, 4]) ~ for.woo[, 6])
jmodelmix.shr <- lm((1 - mix.shr[, 4]) ~ mix.shr[, 6])
jmodelagr.mea <- lm((1 - agr.mea[, 4]) ~ agr.mea[, 6])
jmodelshr.shr <- lm((1 - shr.shr[, 4]) ~ shr.shr[, 6])
jmodeltal.shr <- lm((1 - tal.shr[, 4]) ~ tal.shr[, 6])
```

- Sorensen Estimator
```{r}
smodelfor.woo <- lm((1 - for.woo[, 5]) ~ for.woo[, 6])
smodelmix.shr <- lm((1 - mix.shr[, 5]) ~ mix.shr[, 6])
smodelagr.mea <- lm((1 - agr.mea[, 5]) ~ agr.mea[, 6])
smodelshr.shr <- lm((1 - shr.shr[, 5]) ~ shr.shr[, 6])
smodeltal.shr <- lm((1 - tal.shr[, 5]) ~ tal.shr[, 6])
```

- Short and tall shrubs are together in Shrub (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
par(mfrow=c(3, 2))
plot(for.woo[, 6], 1 - for.woo[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelfor.woo)[[1]], b = coef(jmodelfor.woo)[[2]], col = 2, lwd = 4.5)
plot(for.woo[, 6], 1 - for.woo[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelfor.woo)[[1]], b = coef(smodelfor.woo)[[2]], col = 2, lwd = 4.5)

plot(mix.shr[, 6], 1 - mix.shr[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(jmodelmix.shr)[[1]], b = coef(jmodelmix.shr)[[2]], col = 2, lwd = 4.5)
plot(mix.shr[, 6], 1 - mix.shr[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(smodelmix.shr)[[1]], b = coef(smodelmix.shr)[[2]], col = 2, lwd = 4.5)

plot(agr.mea[, 6], 1 - agr.mea[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelagr.mea)[[1]], b = coef(jmodelagr.mea)[[2]], col = 2, lwd = 4.5)
plot(agr.mea[, 6], 1 - agr.mea[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelagr.mea)[[1]], b = coef(smodelagr.mea)[[2]], col = 2, lwd = 4.5)
```

- Short and tall shrubs are separated (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 10, echo=FALSE}
par(mfrow=c(4, 2))
plot(for.woo[, 6], 1 - for.woo[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelfor.woo)[[1]], b = coef(jmodelfor.woo)[[2]], col = 2, lwd = 4.5)
plot(for.woo[, 6], 1 - for.woo[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelfor.woo)[[1]], b = coef(smodelfor.woo)[[2]], col = 2, lwd = 4.5)

plot(tal.shr[, 6], 1 - tal.shr[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(jmodeltal.shr)[[1]], b = coef(jmodeltal.shr)[[2]], col = 2, lwd = 4.5)
plot(tal.shr[, 6], 1 - tal.shr[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(smodeltal.shr)[[1]], b = coef(smodeltal.shr)[[2]], col = 2, lwd = 4.5)

plot(shr.shr[, 6], 1 - shr.shr[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(jmodelshr.shr)[[1]], b = coef(jmodelshr.shr)[[2]], col = 2, lwd = 4.5)
plot(shr.shr[, 6], 1 - shr.shr[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(smodelshr.shr)[[1]], b = coef(smodelshr.shr)[[2]], col = 2, lwd = 4.5)

plot(agr.mea[, 6], 1 - agr.mea[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelagr.mea)[[1]], b = coef(jmodelagr.mea)[[2]], col = 2, lwd = 4.5)
plot(agr.mea[, 6], 1 - agr.mea[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelagr.mea)[[1]], b = coef(smodelagr.mea)[[2]], col = 2, lwd = 4.5)
```

* Mean Dissimilaritiy for each landscape (with standard deviations)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(for.woo[, 4]), mean(mix.shr[, 4]), mean(agr.mea[, 4]))
m.li <- c(mean(for.woo[, 4]) - sd(for.woo[, 4]), mean(mix.shr[, 4]) - sd(mix.shr[, 4]), mean(agr.mea[, 4]) - sd(agr.mea[, 4]))
m.lu <- c(mean(for.woo[, 4]) + sd(for.woo[, 4]), mean(mix.shr[, 4]) + sd(mix.shr[, 4]), mean(agr.mea[, 4]) + sd(agr.mea[, 4]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c( mean(for.woo[, 5]), mean(mix.shr[, 5]), mean(agr.mea[, 5]))
m.li <- c(mean(for.woo[, 5]) - sd(for.woo[, 5]), mean(mix.shr[, 5]) - sd(mix.shr[, 5]), mean(agr.mea[, 5]) - sd(agr.mea[, 5]))
m.lu <- c(mean(for.woo[, 5]) + sd(for.woo[, 5]), mean(mix.shr[, 5]) + sd(mix.shr[, 5]), mean(agr.mea[, 5]) + sd(agr.mea[, 5]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

* Mean Dissimilarity for each landscape (with tall and short shrub separately)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(for.woo[, 4]), mean(tal.shr[, 4]), mean(shr.shr[, 4]), mean(agr.mea[, 4]))
m.li <- c(mean(for.woo[, 4]) - sd(for.woo[, 4]), mean(tal.shr[, 4]) - sd(tal.shr[, 4]), mean(shr.shr[, 4]) - sd(shr.shr[, 4]), mean(agr.mea[, 4]) - sd(agr.mea[, 4]))
m.lu <- c(mean(for.woo[, 4]) + sd(for.woo[, 4]), mean(tal.shr[, 4]) + sd(tal.shr[, 4]), mean(shr.shr[, 4]) + sd(shr.shr[, 4]), mean(agr.mea[, 4]) + sd(agr.mea[, 4]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c(mean(for.woo[, 5]), mean(tal.shr[, 5]), mean(shr.shr[, 5]), mean(agr.mea[, 5]))
m.li <- c(mean(for.woo[, 5]) - sd(for.woo[, 5]), mean(tal.shr[, 5]) - sd(tal.shr[, 5]), mean(shr.shr[, 5]) - sd(shr.shr[, 5]), mean(agr.mea[, 5]) - sd(agr.mea[, 5]))
m.lu <- c(mean(for.woo[, 5]) + sd(for.woo[, 5]), mean(tal.shr[, 5]) + sd(tal.shr[, 5]), mean(shr.shr[, 5]) + sd(shr.shr[, 5]), mean(agr.mea[, 5]) + sd(agr.mea[, 5]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

**between landscapes**
```{r}
landsc_between <- function(base, s1, s2){
  result <- NULL
  for(i in s1){
    for(j in s2){
      result <- rbind(result, base[(base[, 2] == i & base[, 3] == j) | (base[, 2] == j & base[, 3] == i), ])
    }
  }
  result
}
```

This function creates a database of pairs of biotypes of the same type, but are in different landscapes. Also, I analyzed separately short and tall shrub among landscapes.

```{r}
mea <- landsc_between(b.div.mean, ma, c(mm, mf))
shr <- landsc_between(b.div.mean, sm, c(sa, sf))
tal <- landsc_between(b.div.mean, tm, c(ta, tf))
woo <- landsc_between(b.div.mean, wf, c(wa, wm))
mix <- rbind(shr, tal)
```

**Regreesion models**

- Jaccard Estimator
```{r}
jmodelwoo <- lm((1 - woo[, 4]) ~ woo[, 6])
jmodelmix <- lm((1 - mix[, 4]) ~ mix[, 6])
jmodelmea <- lm((1 - mea[, 4]) ~ mea[, 6])
jmodelshr <- lm((1 - shr[, 4]) ~ shr[, 6])
jmodeltal <- lm((1 - tal[, 4]) ~ tal[, 6])
```

- Sorensen Estimator
```{r}
smodelwoo <- lm((1 - woo[, 5]) ~ woo[, 6])
smodelmix <- lm((1 - mix[, 5]) ~ mix[, 6])
smodelmea <- lm((1 - mea[, 5]) ~ mea[, 6])
smodelshr <- lm((1 - shr[, 5]) ~ shr[, 6])
smodeltal <- lm((1 - tal[, 5]) ~ tal[, 6])
```

- Short and tall shrubs are together in Shrub (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
par(mfrow=c(3, 2))
plot(woo[, 6], 1 - woo[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelwoo)[[1]], b = coef(jmodelwoo)[[2]], col = 2, lwd = 4.5)
plot(woo[, 6], 1 - woo[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelwoo)[[1]], b = coef(smodelwoo)[[2]], col = 2, lwd = 4.5)

plot(mix[, 6], 1 - mix[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(jmodelmix)[[1]], b = coef(jmodelmix)[[2]], col = 2, lwd = 4.5)
plot(mix[, 6], 1 - mix[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(smodelmix)[[1]], b = coef(smodelmix)[[2]], col = 2, lwd = 4.5)

plot(mea[, 6], 1 - mea[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelmea)[[1]], b = coef(jmodelmea)[[2]], col = 2, lwd = 4.5)
plot(mea[, 6], 1 - mea[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelmea)[[1]], b = coef(smodelmea)[[2]], col = 2, lwd = 4.5)
```

- Short and tall shrubs are separated (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 10, echo=FALSE}
par(mfrow=c(4, 2))
plot(woo[, 6], 1 - woo[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelwoo)[[1]], b = coef(jmodelwoo)[[2]], col = 2, lwd = 4.5)
plot(woo[, 6], 1 - woo[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelwoo)[[1]], b = coef(smodelwoo)[[2]], col = 2, lwd = 4.5)

plot(tal[, 6], 1 - tal[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(jmodeltal)[[1]], b = coef(jmodeltal)[[2]], col = 2, lwd = 4.5)
plot(tal[, 6], 1 - tal[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(smodeltal)[[1]], b = coef(smodeltal)[[2]], col = 2, lwd = 4.5)

plot(shr[, 6], 1 - shr[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(jmodelshr)[[1]], b = coef(jmodelshr)[[2]], col = 2, lwd = 4.5)
plot(shr[, 6], 1 - shr[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(smodelshr)[[1]], b = coef(smodelshr)[[2]], col = 2, lwd = 4.5)

plot(mea[, 6], 1 - mea[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelmea)[[1]], b = coef(jmodelmea)[[2]], col = 2, lwd = 4.5)
plot(mea[, 6], 1 - mea[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelmea)[[1]], b = coef(smodelmea)[[2]], col = 2, lwd = 4.5)
```

* Mean Dissimilarity for each landscape (with standard deviations)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(woo[, 4]), mean(mix[, 4]), mean(mea[, 4]) )
m.li <- c(mean(woo[, 4]) - sd(woo[, 4]), mean(mix[, 4]) - sd(mix[, 4]), mean(mea[, 4]) - sd(mea[, 4]))
m.lu <- c(mean(woo[, 4]) + sd(woo[, 4]), mean(mix[, 4]) + sd(mix[, 4]), mean(mea[, 4]) + sd(mea[, 4]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c(mean(woo[, 5]), mean(mix[, 5]), mean(mea[, 5]) )
m.li <- c(mean(woo[, 5]) - sd(woo[, 5]), mean(mix[, 5]) - sd(mix[, 5]), mean(mea[, 5]) - sd(mea[, 5]))
m.lu <- c(mean(woo[, 5]) + sd(woo[, 5]), mean(mix[, 5]) + sd(mix[, 5]), mean(mea[, 5]) + sd(mea[, 5]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

* Mean Dissimilarity for each landscape (with tall and short shrub separately)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(woo[, 4]), mean(tal[, 4]), mean(shr[, 4]), mean(mea[, 4]) )
m.li <- c(mean(woo[, 4]) - sd(woo[, 4]), mean(tal[, 4]) - sd(tal[, 4]), mean(shr[, 4]) - sd(shr[, 4]), mean(mea[, 4]) - sd(mea[, 4]))
m.lu <- c(mean(woo[, 4]) + sd(woo[, 4]), mean(tal[, 4]) + sd(tal[, 4]), mean(shr[, 4]) + sd(shr[, 4]), mean(mea[, 4]) + sd(mea[, 4]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c(mean(woo[, 5]), mean(tal[, 5]), mean(shr[, 5]), mean(mea[, 5]) )
m.li <- c(mean(woo[, 5]) - sd(woo[, 5]), mean(tal[, 5]) - sd(tal[, 5]), mean(shr[, 5]) - sd(shr[, 5]), mean(mea[, 5]) - sd(mea[, 5]))
m.lu <- c(mean(woo[, 5]) + sd(woo[, 5]), mean(tal[, 5]) + sd(tal[, 5]), mean(shr[, 5]) + sd(shr[, 5]), mean(mea[, 5]) + sd(mea[, 5]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

**Biotopes**
```{r}
mfma <- c(mf, mm, ma)
sfma <- c(sf, sm, sa)
tfma <- c(tf, tm, ta)
wfma <- c(wf, wm, wa)
mixf <- c(sf, sm, sa, tf, tm, ta)
```

This function creates databse for each biotope independent landscape.

```{r}
mea.bio <- landsc_within(b.div.mean, mfma, mfma)
sho.bio <- landsc_within(b.div.mean, sfma, sfma)
tal.bio <- landsc_within(b.div.mean, tfma, tfma)
woo.bio <- landsc_within(b.div.mean, wfma, wfma)
mix.bio <- landsc_within(b.div.mean, mixf, mixf)
```

**Regression models**

- Jaccard Estimator
```{r}
jmodelwoo.bio <- lm((1 - woo.bio[, 4]) ~ woo.bio[, 6])
jmodelmix.bio <- lm((1 - mix.bio[, 4]) ~ mix.bio[, 6])
jmodelmea.bio <- lm((1 - mea.bio[, 4]) ~ mea.bio[, 6])
jmodelsho.bio <- lm((1 - sho.bio[, 4]) ~ sho.bio[, 6])
jmodeltal.bio <- lm((1 - tal.bio[, 4]) ~ tal.bio[, 6])
```

- Sorensen Estimator
```{r}
smodelwoo.bio <- lm((1 - woo.bio[, 5]) ~ woo.bio[, 6])
smodelmix.bio <- lm((1 - mix.bio[, 5]) ~ mix.bio[, 6])
smodelmea.bio <- lm((1 - mea.bio[, 5]) ~ mea.bio[, 6])
smodelsho.bio <- lm((1 - sho.bio[, 5]) ~ sho.bio[, 6])
smodeltal.bio <- lm((1 - tal.bio[, 5]) ~ tal.bio[, 6])
```

- Short and tall shrubs are together (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
par(mfrow=c(3, 2))
plot(woo.bio[, 6], 1 - woo.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelwoo.bio)[[1]], b = coef(jmodelwoo.bio)[[2]], col = 2, lwd = 4.5)
plot(woo.bio[, 6], 1 - woo.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelwoo.bio)[[1]], b = coef(smodelwoo.bio)[[2]], col = 2, lwd = 4.5)

plot(mix.bio[, 6], 1 - mix.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(jmodelmix.bio)[[1]], b = coef(jmodelmix.bio)[[2]], col = 2, lwd = 4.5)
plot(mix.bio[, 6], 1 - mix.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(smodelmix.bio)[[1]], b = coef(smodelmix.bio)[[2]], col = 2, lwd = 4.5)

plot(mea.bio[, 6], 1 - mea.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelmea.bio)[[1]], b = coef(jmodelmea.bio)[[2]], col = 2, lwd = 4.5)
plot(mea.bio[, 6], 1 - mea.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelmea.bio)[[1]], b = coef(smodelmea.bio)[[2]], col = 2, lwd = 4.5)
```

- Short and tall shrubs are separated (right side: Jaccard and left side: Sorensen)
```{r, fig.width = 10, fig.height = 10, echo=FALSE}
par(mfrow=c(4, 2))
plot(woo.bio[, 6], 1 - woo.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jmodelwoo.bio)[[1]], b = coef(jmodelwoo.bio)[[2]], col = 2, lwd = 4.5)
plot(woo.bio[, 6], 1 - woo.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(smodelwoo.bio)[[1]], b = coef(smodelwoo.bio)[[2]], col = 2, lwd = 4.5)

plot(tal.bio[, 6], 1 - tal.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(jmodeltal.bio)[[1]], b = coef(jmodeltal.bio)[[2]], col = 2, lwd = 4.5)
plot(tal.bio[, 6], 1 - tal.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(a = coef(smodeltal.bio)[[1]], b = coef(smodeltal.bio)[[2]], col = 2, lwd = 4.5)

plot(sho.bio[, 6], 1 - sho.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(jmodelsho.bio)[[1]], b = coef(jmodelsho.bio)[[2]], col = 2, lwd = 4.5)
plot(sho.bio[, 6], 1 - sho.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(a = coef(smodelsho.bio)[[1]], b = coef(smodelsho.bio)[[2]], col = 2, lwd = 4.5)

plot(mea.bio[, 6], 1 - mea.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(jmodelmea.bio)[[1]], b = coef(jmodelmea.bio)[[2]], col = 2, lwd = 4.5)
plot(mea.bio[, 6], 1 - mea.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(a = coef(smodelmea.bio)[[1]], b = coef(smodelmea.bio)[[2]], col = 2, lwd = 4.5)
```

* Mean Dissimilarity for each landscape (with standard deviations)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(woo.bio[, 4]), mean(mix.bio[, 4]), mean(mea.bio[, 4]))
m.li <- c(mean(woo.bio[, 4]) - sd(woo.bio[, 4]), mean(mix.bio[, 4]) - sd(mix.bio[, 4]), mean(mea.bio[, 4]) - sd(mea.bio[, 4]))
m.lu <- c(mean(woo.bio[, 4]) + sd(woo.bio[, 4]), mean(mix.bio[, 4]) + sd(mix.bio[, 4]), mean(mea.bio[, 4]) + sd(mea.bio[, 4]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c( mean(woo.bio[, 5]), mean(mix.bio[, 5]), mean(mea.bio[, 5]))
m.li <- c(mean(woo.bio[, 5]) - sd(woo.bio[, 5]), mean(mix.bio[, 5]) - sd(mix.bio[, 5]), mean(mea.bio[, 5]) - sd(mea.bio[, 5]))
m.lu <- c(mean(woo.bio[, 5]) + sd(woo.bio[, 5]), mean(mix.bio[, 5]) + sd(mix.bio[, 5]), mean(mea.bio[, 5]) + sd(mea.bio[, 5]))
plot(1:3, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
segments(x0 = 1:3, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

* Mean Dissimilarity for each landscape (with tall and short shrubs separately)
```{r}
par(mfrow=c(1, 2))
m.data <- c(mean(woo.bio[, 4]), mean(tal.bio[, 4]), mean(sho.bio[, 4]), mean(mea.bio[, 4]))
m.li <- c(mean(woo.bio[, 4]) - sd(woo.bio[, 4]), mean(tal.bio[, 4]) - sd(tal.bio[, 4]), mean(sho.bio[, 4]) - sd(sho.bio[, 4]), mean(mea.bio[, 4]) - sd(mea.bio[, 4]))
m.lu <- c(mean(woo.bio[, 4]) + sd(woo.bio[, 4]), mean(tal.bio[, 4]) + sd(tal.bio[, 4]), mean(sho.bio[, 4]) + sd(sho.bio[, 4]), mean(mea.bio[, 4]) + sd(mea.bio[, 4]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Jaccard adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)

m.data <- c(mean(woo.bio[, 5]), mean(tal.bio[, 5]), mean(sho.bio[, 5]), mean(mea.bio[, 5]))
m.li <- c(mean(woo.bio[, 5]) - sd(woo.bio[, 5]), mean(tal.bio[, 5]) - sd(tal.bio[, 5]), mean(sho.bio[, 5]) - sd(sho.bio[, 5]), mean(mea.bio[, 5]) - sd(mea.bio[, 5]))
m.lu <- c(mean(woo.bio[, 5]) + sd(woo.bio[, 5]), mean(tal.bio[, 5]) + sd(tal.bio[, 5]), mean(sho.bio[, 5]) + sd(sho.bio[, 5]), mean(mea.bio[, 5]) + sd(mea.bio[, 5]))
plot(1:4, 1 - m.data, xaxt = "n", ylim=c(0, 1), xlab = "", ylab = expression(~beta*"-diversity"), main = "Sorensen adjusted")
axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Meadow"))
segments(x0 = 1:4, y0 = 1 - m.li, y1 = 1 - m.lu, col = 1)
```

* Mean Dissimilarity for each scale
```{r, fig.width = 10, fig.height = 8, echo=FALSE}
par(mfrow=c(3, 2))
plot(woo.bio[, 6], 1 - woo.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(woo.bio[woo.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 445) & (woo.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 1810) & (woo.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(woo.bio[(woo.bio[, 6] > 1811), 4]), 5690), col = 2, lwd = 4.5)
plot(woo.bio[, 6], 1 - woo.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(woo.bio[woo.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 445) & (woo.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 1810) & (woo.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(woo.bio[(woo.bio[, 6] > 1811), 5]), 5690), col = 2, lwd = 4.5)

plot(mix.bio[, 6], 1 - mix.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mix.bio[mix.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mix.bio[(mix.bio[, 6] <= 445) & (mix.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mix.bio[(mix.bio[, 6] <= 1810) & (mix.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mix.bio[(mix.bio[, 6] > 1811), 4]), 5690), col = 2, lwd = 4.5)
plot(mix.bio[, 6], 1 - mix.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mix.bio[mix.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mix.bio[(mix.bio[, 6] <= 445) & (mix.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mix.bio[(mix.bio[, 6] <= 1810) & (mix.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mix.bio[(mix.bio[, 6] > 1811), 5]), 5690), col = 2, lwd = 4.5)

plot(mea.bio[, 6], 1 - mea.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mea.bio[mea.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 445) & (mea.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 1810) & (mea.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mea.bio[(mea.bio[, 6] > 1810), 4]), 5690), col = 2, lwd = 4.5)
plot(mea.bio[, 6], 1 - mea.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mea.bio[mea.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 445) & (mea.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 1810) & (mea.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mea.bio[(mea.bio[, 6] > 1810), 5]), 5690), col = 2, lwd = 4.5)
```

* Mean Dissimilarity for each scale (with tall and short shrubs separately)
```{r, fig.width = 10, fig.height = 10, echo=FALSE}
par(mfrow=c(4, 2))
plot(woo.bio[, 6], 1 - woo.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(woo.bio[woo.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 445) & (woo.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 1810) & (woo.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(woo.bio[(woo.bio[, 6] > 1811), 4]), 5690), col = 2, lwd = 4.5)
plot(woo.bio[, 6], 1 - woo.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Forest")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(woo.bio[woo.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 445) & (woo.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(woo.bio[(woo.bio[, 6] <= 1810) & (woo.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(woo.bio[(woo.bio[, 6] > 1811), 5]), 5690), col = 2, lwd = 4.5)

plot(tal.bio[, 6], 1 - tal.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(tal.bio[tal.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(tal.bio[(tal.bio[, 6] <= 445) & (tal.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(tal.bio[(tal.bio[, 6] <= 1810) & (tal.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(tal.bio[(tal.bio[, 6] > 1811), 4]), 5690), col = 2, lwd = 4.5)
plot(tal.bio[, 6], 1 - tal.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Tall")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(tal.bio[tal.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(tal.bio[(tal.bio[, 6] <= 445) & (tal.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(tal.bio[(tal.bio[, 6] <= 1810) & (tal.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(tal.bio[(tal.bio[, 6] > 1811), 5]), 5690), col = 2, lwd = 4.5)

plot(sho.bio[, 6], 1 - sho.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(sho.bio[sho.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(sho.bio[(sho.bio[, 6] <= 445) & (sho.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(sho.bio[(sho.bio[, 6] <= 1810) & (sho.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(sho.bio[(sho.bio[, 6] > 1811), 4]), 5690), col = 2, lwd = 4.5)
plot(sho.bio[, 6], 1 - sho.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Short")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(sho.bio[sho.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(sho.bio[(sho.bio[, 6] <= 445) & (sho.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(sho.bio[(sho.bio[, 6] <= 1810) & (sho.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(sho.bio[(sho.bio[, 6] > 1811), 5]), 5690), col = 2, lwd = 4.5)

plot(mea.bio[, 6], 1 - mea.bio[, 4], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mea.bio[mea.bio[, 6] <= 115, 4]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 445) & (mea.bio[, 6] > 115), 4]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 1810) & (mea.bio[, 6] > 445), 4]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mea.bio[(mea.bio[, 6] > 1810), 4]), 5690), col = 2, lwd = 4.5)
plot(mea.bio[, 6], 1 - mea.bio[, 5], ylim = c(0, 1), xlim = c(0, 7500), xlab = "Geographic Distance (m)", ylab = expression(~beta*"-diversity"), main = "Meadow")
abline(v = c(115, 455, 1810), col = "gray", lwd = 1.5, lty = 2)
lines(1:115, rep(1 - mean(mea.bio[mea.bio[, 6] <= 115, 5]), 115), col = 2, lwd = 4.5)
lines(116:445, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 445) & (mea.bio[, 6] > 115), 5]), 330), col = 2, lwd = 4.5)
lines(446:1810, rep(1 - mean(mea.bio[(mea.bio[, 6] <= 1810) & (mea.bio[, 6] > 445), 5]), 1365), col = 2, lwd = 4.5)
lines(1811:7500, rep(1 - mean(mea.bio[(mea.bio[, 6] > 1810), 5]), 5690), col = 2, lwd = 4.5)
```

## Bootstrapping
```{r}
library(boot)
# function to obtain regression weights 
bs.jac <- function(formula, data, ind){
  d <- data[ind,] # allows boot to select sample
  fit <- lm(formula, data = d)
  return(c(coef(fit), summary(fit)$r.square, mean(d[, 4]))) 
} 

bs.sor <- function(formula, data, ind){
  d <- data[ind,] # allows boot to select sample
  fit <- lm(formula, data = d)
  return(c(coef(fit), summary(fit)$r.square, mean(d[, 5]))) 
} 
```

* Within Landscape
```{r}
# bootstrapping with 2000 replications
wl.jforres <- boot(data = as.data.frame(for.woo), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
wl.sforres <- boot(data = as.data.frame(for.woo), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

wl.jmixres <- boot(data = as.data.frame(mix.shr), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
wl.smixres <- boot(data = as.data.frame(mix.shr), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

wl.jtalres <- boot(data = as.data.frame(tal.shr), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
wl.stalres <- boot(data = as.data.frame(tal.shr), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

wl.jshrres <- boot(data = as.data.frame(shr.shr), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
wl.sshrres <- boot(data = as.data.frame(shr.shr), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

wl.jmeares <- boot(data = as.data.frame(agr.mea), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
wl.smeares <- boot(data = as.data.frame(agr.mea), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)
```

* Between Landscapes
```{r}
# bootstrapping with 2000 replications
bl.jwoores <- boot(data = as.data.frame(woo), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
bl.swoores <- boot(data = as.data.frame(woo), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

bl.jmixres <- boot(data = as.data.frame(mix), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
bl.smixres <- boot(data = as.data.frame(mix), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

bl.jtalres <- boot(data = as.data.frame(tal), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
bl.stalres <- boot(data = as.data.frame(tal), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

bl.jshrres <- boot(data = as.data.frame(shr), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
bl.sshrres <- boot(data = as.data.frame(shr), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

bl.jmeares <- boot(data = as.data.frame(mea), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
bl.smeares <- boot(data = as.data.frame(mea), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)
```

* All Biotopes
```{r}
# bootstrapping with 2000 replications
al.jforres <- boot(data = as.data.frame(woo.bio), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
al.sforres <- boot(data = as.data.frame(woo.bio), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

al.jmixres <- boot(data = as.data.frame(mix.bio), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
al.smixres <- boot(data = as.data.frame(mix.bio), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

al.jtalres <- boot(data = as.data.frame(tal.bio), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
al.stalres <- boot(data = as.data.frame(tal.bio), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

al.jshrres <- boot(data = as.data.frame(sho.bio), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
al.sshrres <- boot(data = as.data.frame(sho.bio), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)

al.jmeares <- boot(data = as.data.frame(mea.bio), statistic = bs.jac, R = 2000, formula = (1 - Jabd) ~ ipcc)
al.smeares <- boot(data = as.data.frame(mea.bio), statistic = bs.sor, R = 2000, formula = (1 - Labd) ~ ipcc)
```

**Confidence Interval**
```{r, echo=FALSE}
ci.boot <- function(base){
  temp1 <- boot.ci(base, type="bca", index=1) # intercept 
  temp2 <- boot.ci(base, type="bca", index=2) # slope
  temp3 <- boot.ci(base, type="bca", index=3) # r.square
  temp4 <- boot.ci(base, type="bca", index=4) # mean
  base.ci <- rbind(cbind(temp1$t0, temp1$bca[4], temp1$bca[5]), cbind(temp2$t0, temp2$bca[4], temp2$bca[5]), cbind(temp3$t0, temp3$bca[4], temp3$bca[5]), cbind(temp4$t0, temp4$bca[4], temp4$bca[5]))
  base.ci
}
```

* Within Landscape - get 95% confidence intervals

*Jaccard Estimator*
```{r}
wl.jforres.ci <- ci.boot(wl.jforres)
wl.jmixres.ci <- ci.boot(wl.jmixres)
wl.jtalres.ci <- ci.boot(wl.jtalres)
wl.jshrres.ci <- ci.boot(wl.jshrres)
wl.jmeares.ci <- ci.boot(wl.jmeares)
```

*Sorensen Estimator*
```{r}
wl.sforres.ci <- ci.boot(wl.sforres)
wl.smixres.ci <- ci.boot(wl.smixres)
wl.stalres.ci <- ci.boot(wl.stalres)
wl.sshrres.ci <- ci.boot(wl.sshrres)
wl.smeares.ci <- ci.boot(wl.smeares)
```

* Between Landscapes - get 95% confidence intervals

*Jaccard Estimator*
```{r}
bl.jforres.ci <- ci.boot(bl.jwoores)
bl.jmixres.ci <- ci.boot(bl.jmixres)
bl.jtalres.ci <- ci.boot(bl.jtalres)
bl.jshrres.ci <- ci.boot(bl.jshrres)
bl.jmeares.ci <- ci.boot(bl.jmeares)
```

*Sorensen Estimator*
```{r}
bl.sforres.ci <- ci.boot(bl.swoores)
bl.smixres.ci <- ci.boot(bl.smixres)
bl.stalres.ci <- ci.boot(bl.stalres)
bl.sshrres.ci <- ci.boot(bl.sshrres)
bl.smeares.ci <- ci.boot(bl.smeares)
```

* All Biotopes - get 95% confidence intervals

*Jaccard Estimator*
```{r}
al.jforres.ci <- ci.boot(al.jforres)
al.jmixres.ci <- ci.boot(al.jmixres)
al.jtalres.ci <- ci.boot(al.jtalres)
al.jshrres.ci <- ci.boot(al.jshrres)
al.jmeares.ci <- ci.boot(al.jmeares)
```

*Sorensen Estimator*
```{r}
al.sforres.ci <- ci.boot(al.sforres)
al.smixres.ci <- ci.boot(al.smixres)
al.stalres.ci <- ci.boot(al.stalres)
al.sshrres.ci <- ci.boot(al.sshrres)
al.smeares.ci <- ci.boot(al.smeares)
```
---

## Results 1
```{r, echo=FALSE}
interc.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[1, 1], base2[1, 1], base3[1, 1])
  l.ci <- c(base1[1, 2], base2[1, 2], base3[1, 2])
  s.ci <- c(base1[1, 3], base2[1, 3], base3[1, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim =c(0, 1), ylab = "Intercept", xlab = "", pch = "-", lwd = 2)
  #title("All Years - Jaccard Estimator", outer = TRUE, cex = 1.5)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Agric"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

dissim.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[4, 1], base2[4, 1], base3[4, 1])
  l.ci <- c(base1[4, 2], base2[4, 2], base3[4, 2])
  s.ci <- c(base1[4, 3], base2[4, 3], base3[4, 3])
  plot(1:3, 1 - mean.ci, xaxt = "n", ylim =c(0, 1), ylab = expression(~beta*"-diversity"), xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Agric"))
  segments(x0 = 1:3, y0 = 1 - l.ci, y1 = 1 - s.ci)
  points(1:3, 1 - l.ci, lwd = 1.5, pch = "-")
  points(1:3, 1 - s.ci, lwd = 1.5, pch = "-")
}

slope.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[2, 1], base2[2, 1], base3[2, 1])
  l.ci <- c(base1[2, 2], base2[2, 2], base3[2, 2])
  s.ci <- c(base1[2, 3], base2[2, 3], base3[2, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "Slope", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Agric"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

rsquar.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[3, 1], base2[3, 1], base3[3, 1])
  l.ci <- c(base1[3, 2], base2[3, 2], base3[3, 2])
  s.ci <- c(base1[3, 3], base2[3, 3], base3[3, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "R-Square", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Agric"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

interc.plot4 <- function(base1, base2, base3, base4){
  mean.ci <- c(base1[1, 1], base2[1, 1], base3[1, 1], base4[1, 1])
  l.ci <- c(base1[1, 2], base2[1, 2], base3[1, 2], base4[1, 2])
  s.ci <- c(base1[1, 3], base2[1, 3], base3[1, 3], base4[1, 3])
  plot(1:4, mean.ci, xaxt = "n", ylim =c(0, 1), ylab = "Intercept", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Agric"))
  segments(x0 = 1:4, y0 = l.ci, y1 = s.ci)
  points(1:4, l.ci, lwd = 1.5, pch = "-")
  points(1:4, s.ci, lwd = 1.5, pch = "-")
}

dissim.plot4 <- function(base1, base2, base3, base4){
  mean.ci <- c(base1[4, 1], base2[4, 1], base3[4, 1], base4[4, 1])
  l.ci <- c(base1[4, 2], base2[4, 2], base3[4, 2], base4[4, 2])
  s.ci <- c(base1[4, 3], base2[4, 3], base3[4, 3], base4[4, 3])
  plot(1:4, 1 - mean.ci, xaxt = "n", ylim =c(0, 1), ylab = expression(~beta*"-diversity"), xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Agric"))
  segments(x0 = 1:4, y0 = 1 - l.ci, y1 = 1 - s.ci)
  points(1:4, 1 - l.ci, lwd = 1.5, pch = "-")
  points(1:4, 1 - s.ci, lwd = 1.5, pch = "-")
}

slope.plot4 <- function(base1, base2, base3, base4){
  mean.ci <- c(base1[2, 1], base2[2, 1], base3[2, 1], base4[2, 1])
  l.ci <- c(base1[2, 2], base2[2, 2], base3[2, 2], base4[2, 2])
  s.ci <- c(base1[2, 3], base2[2, 3], base3[2, 3], base4[2, 3])
  plot(1:4, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "Slope", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Agric"))
  segments(x0 = 1:4, y0 = l.ci, y1 = s.ci)
  points(1:4, l.ci, lwd = 1.5, pch = "-")
  points(1:4, s.ci, lwd = 1.5, pch = "-")
}

rsquar.plot4 <- function(base1, base2, base3, base4){
  mean.ci <- c(base1[3, 1], base2[3, 1], base3[3, 1], base4[3, 1])
  l.ci <- c(base1[3, 2], base2[3, 2], base3[3, 2], base4[3, 2])
  s.ci <- c(base1[3, 3], base2[3, 3], base3[3, 3], base4[3, 3])
  plot(1:4, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "R-Square", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:4, labels = c("Forest", "Tall", "Short", "Agric"))
  segments(x0 = 1:4, y0 = l.ci, y1 = s.ci)
  points(1:4, l.ci, lwd = 1.5, pch = "-")
  points(1:4, s.ci, lwd = 1.5, pch = "-")
}
```

**Jaccard**

* Intercept
```{r, fig.width = 10}
par(mfrow = c(1, 3))
interc.plot3(wl.jforres.ci, wl.jmixres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
interc.plot3(bl.jforres.ci, bl.jmixres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
interc.plot3(al.jforres.ci, al.jmixres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* Dissimilarity
```{r, fig.width = 10}
par(mfrow = c(1, 3))
dissim.plot3(wl.jforres.ci, wl.jmixres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
dissim.plot3(bl.jforres.ci, bl.jmixres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
dissim.plot3(al.jforres.ci, al.jmixres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* Slope
```{r, fig.width = 10}
par(mfrow = c(1, 3))
slope.plot3(wl.jforres.ci, wl.jmixres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
slope.plot3(bl.jforres.ci, bl.jmixres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
slope.plot3(al.jforres.ci, al.jmixres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* R-Square
```{r, fig.width = 10}
par(mfrow = c(1, 3))
rsquar.plot3(wl.jforres.ci, wl.jmixres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
rsquar.plot3(bl.jforres.ci, bl.jmixres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
rsquar.plot3(al.jforres.ci, al.jmixres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

**Sorensen**

* Intercept
```{r, fig.width = 10}
par(mfrow = c(1, 3))
interc.plot3(wl.sforres.ci, wl.smixres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
interc.plot3(bl.sforres.ci, bl.smixres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
interc.plot3(al.sforres.ci, al.smixres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

* Dissimilarity
```{r, fig.width = 10}
par(mfrow = c(1, 3))
dissim.plot3(wl.sforres.ci, wl.smixres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
dissim.plot3(bl.sforres.ci, bl.smixres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
dissim.plot3(al.sforres.ci, al.smixres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

* Slope
```{r, fig.width = 10}
par(mfrow = c(1, 3))
slope.plot3(wl.sforres.ci, wl.smixres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
slope.plot3(bl.sforres.ci, bl.smixres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
slope.plot3(al.sforres.ci, al.smixres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

* R-Square
```{r, fig.width = 10}
par(mfrow = c(1, 3))
rsquar.plot3(wl.sforres.ci, wl.smixres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
rsquar.plot3(bl.sforres.ci, bl.smixres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
rsquar.plot3(al.sforres.ci, al.smixres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

# Results 2

**Jaccard**
* Intercept
```{r, fig.width = 10}
par(mfrow = c(1, 3))
interc.plot4(wl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
interc.plot4(bl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
interc.plot4(al.jforres.ci, al.jtalres.ci, al.jshrres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* Dissimilarity
```{r, fig.width = 10}
par(mfrow = c(1, 3))
dissim.plot4(wl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
dissim.plot4(bl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
dissim.plot4(al.jforres.ci, al.jtalres.ci, al.jshrres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* Slope
```{r, fig.width = 10}
par(mfrow = c(1, 3))
slope.plot4(wl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
slope.plot4(bl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
slope.plot4(al.jforres.ci, al.jtalres.ci, al.jshrres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

* R-Square
```{r, fig.width = 10}
par(mfrow = c(1, 3))
rsquar.plot4(wl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, wl.jmeares.ci)
title("Within Landscape", cex = 1.5)
rsquar.plot4(bl.jforres.ci, wl.jtalres.ci, wl.jshrres.ci, bl.jmeares.ci)
title("Between Landscapes", cex = 1.5)
rsquar.plot4(al.jforres.ci, al.jtalres.ci, al.jshrres.ci, al.jmeares.ci)
title("All Biotopes", cex = 1.5)
```

**Sorensen**

* Intercept
```{r, fig.width = 10}
par(mfrow = c(1, 3))
interc.plot4(wl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
interc.plot4(bl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
interc.plot4(al.sforres.ci, al.stalres.ci, al.sshrres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

* Dissimilarity
```{r, fig.width = 10}
par(mfrow = c(1, 3))
dissim.plot4(wl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
dissim.plot4(bl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
dissim.plot4(al.sforres.ci, al.stalres.ci, al.sshrres.ci, al.smeares.ci)
```

* Slope
```{r, fig.width = 10}
par(mfrow = c(1, 3))
slope.plot4(wl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
slope.plot4(bl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
slope.plot4(al.sforres.ci, al.stalres.ci, al.sshrres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```

* R-Square
```{r, fig.width = 10}
par(mfrow = c(1, 3))
rsquar.plot4(wl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, wl.smeares.ci)
title("Within Landscape", cex = 1.5)
rsquar.plot4(bl.sforres.ci, wl.stalres.ci, wl.sshrres.ci, bl.smeares.ci)
title("Between Landscapes", cex = 1.5)
rsquar.plot4(al.sforres.ci, al.stalres.ci, al.sshrres.ci, al.smeares.ci)
title("All Biotopes", cex = 1.5)
```