---
title: "Moth"
author: "Murilo Miranda"
date: "11 Sep 2014"
output: pdf_document
---


## Load Data and Codes
* Read dataset with id, site, period, species, abund

```{r loaddata}
data <- read.csv("data.csv", h = T)
head(data)

library(xtable)
library(boot)
source('chao.R')
source('distanc.R')
```


## Distances
The distances between pairs were calculated using QGIS for IPCC and IGeoE:

* Hayford Gauss IPCC: 

```{r ipcc}
dist <- read.csv("dist_mat_ipcc.csv", h = T)
dist <- dist[-1]
DIST1 <- distanc(dist)
head(DIST1)
```

* Hayford Gauss IGeoE

```{r igeoe}
dist <- read.csv("dist_mat_igeoe.csv", h = T)
dist <- dist[-1]
DIST2 <- distanc(dist)
head(DIST2)
```

```{r histdistanc}
par(mfrow=c(2, 1))
hist(DIST1[, 3], main = "IPCC", xlab = "Geographic distance (m)", ylab = "Frequency")
hist(DIST2[, 3], main = "IGEOE", xlab = "Geographic distance (m)", ylab = "Frequency")
```

The histograms have the same behavior, then I chose the first vector of distances (IPCC) for analysing the data.

## Data
Sorensen and Jaccard Estimators were estimated using unseen species (Chao et al 2005). The data-set was subseted by sample. Variables created from the chao-function have the following columns:

```{r calcbeta}
sample1 <- chao(1, 1, "sample1")
sample2 <- chao(2, 2, "sample2")
sample3 <- chao(3, 3, "sample3")
sample4 <- chao(4, 4, "sample4")
sample5 <- chao(5, 5, "sample5")
sample6 <- chao(6, 6, "sample6")
```

 - p: sampling period.
 - s1: the code of sample 1. 
 - s2: the code of sample 2.
 - n: the number of observed species in the sample 1.
 - nsp1: the number of species in the sample 1.
 - m: the number of observed species in the sample 2.
 - nsp2: the number of species in the sample 2.
 - nsh: the number of observed shared species in the two samples.
 - fm1: the observed number of shared species that occur once in sample 2.
 - fm2: the observed number of shared species that occur twice in sample 2.
 - f1m: the observed number of shared species that occur once in sample 1.
 - f2m: the observed number of shared species that occur twice in sample 1.
 - u_pt1: abundance sum of shared species divided by species number for the sample 1.
 - v_pt1: abundance sum of shared species divided by species number for the sample 2.
 - Junad: Jaccard unadjusted estimator.
 - Lunad: Sorensen unadjusted estimator.
 - U: u_pt1 plus unseen species for the sample 2.
 - V: v_pt1 plus unseen species for the sample 1.
 - Jabd: Jaccard adjusted estimator.
 - Labd: Sorensen adjusted estimator.

```{r}
head(sample1)
```


## Exploratory Analysis
These functions were used to synthesize the samples for each year. Moth samplings were conducted for two years (2011 and 2012), each year had three sampling period.

```{r}
trisamples <- function(base1, base2, base3, vr){
  base <- matrix(0, nrow = dim(base1)[1])
  for(i in 1:dim(base1)[1]){
    base[i] <- (base1[i, vr] + base2[i, vr] + base3[i, vr])/3
  }
  base
}

bisamples <- function(base1, base2){
  base <- matrix(0, nrow = length(base1))
  for(i in 1:length(base1)){
    base[i] <- (base1[i] + base2[i])/2
  }
  base
}
```

* Calculated the dissimilarity average per site for first year

```{r}
Jperiod1 <- trisamples(sample1, sample2, sample3, 19)
Lperiod1 <- trisamples(sample1, sample2, sample3, 20)
```

```{r firstyear, fig.width = 12}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod1), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod1), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Sorensen")
```

* Calculated the dissimilarity average per site for second year

```{r}
Jperiod2 <- trisamples(sample4, sample5, sample6, 19)
Lperiod2 <- trisamples(sample4, sample5, sample6, 20)
```

```{r secondyear, fig.width = 12}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod2), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod2), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Sorensen")
```

* Calculated the dissimilarity average per site for both years

```{r}
Jperiod <- bisamples(Jperiod1, Jperiod2)
Lperiod <- bisamples(Lperiod1, Lperiod2)
```

```{r allyears, fig.width = 12}
par(mfrow=c(1, 2))
plot(DIST1[, 3], (1 - Jperiod), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Jaccard")
plot(DIST1[, 3], (1 - Lperiod), ylim = c(0, 1), xlab = "Geographic Distance (m)", ylab = 
       expression(~beta*"-diversity"), main = "Sorensen")
```

**DATASET**: I created a new database with six columns:

  - p: no functionality, I created just to standardize with other functions previously created. 
  - s1: site 1
  - s2: site 2
  - Jabd: Jaccard adjusted estimator
  - Labd: Sorensen adjusted estimator
  - ipcc: distance between site 1 and site 2 (Hayford Gauss IPCC)

```{r setdata}
b.div.mean <- cbind(sample1[, 1], sample1[, 2], sample1[, 3], Jperiod, Lperiod, DIST1[, 3])
colnames(b.div.mean) <- c("p", "s1", "s2", "Jabd", "Labd", "ipcc")

head(b.div.mean)
```

Samples were taken in three landscapes that represent the farmland abandonment gradient: meadow-dominated, shrub-dominated and forest-dominated. In each landscape had 28 fixed sampling sites divided into four biotopes (meadow, short shrub, tall shrub and woodland), totaling 84 sampling sites.

* forest-dominated:

```{r}
mf <- c(56) #m - meadow
sf <- c(36, 39, 42, 45, 46) #s - short shrub
tf <- c(34, 49) #t - tall shrub
wf <- c(29, 30, 31, 32, 33, 35, 37, 38, 40, 41, 43, 44, 47, 48, 50, 51, 52, 53, 54, 55) 
#w - woodland
```
* shrub-dominated (m - mixed)

```{r}
mm <- c(68, 75, 77, 84)
sm <- c(60, 64, 65, 66, 67, 70, 78, 79, 82)
tm <- c(57, 58, 59, 61, 62, 63, 69, 71, 72, 74, 76)
wm <- c(73, 80, 81, 83)
```
* meadow-dominated (a - agriculture)

```{r}
ma <- c(1, 9, 14, 15, 16, 17, 18, 19, 21, 23, 24, 25, 27)
sa <- c(2, 8, 10, 11, 12, 13, 20)
ta <- c(3, 4, 5, 6, 7, 28)
wa <- c(22, 26)
```

# FIRST APROARCH

## Within landscape
```{r}
landsc_within <- function(base, s1, s2){
  result <- NULL
  for(i in s1){
    for(j in s2){
      if(i != j){
        result <- rbind(result, base[base[, 2] == i & base[, 3] == j, ])
      }
    }
  }
  result
}
```

```{r}
idmea <- c(ma, sa, ta, wa)
idmix <- c(mm, sm, tm, wm)
idfor <- c(mf, sf, tf, wf)
```

```{r}
m.mea <- landsc_within(b.div.mean, idmea, idmea)
m.mix <- landsc_within(b.div.mean, idmix, idmix)
m.for <- landsc_within(b.div.mean, idfor, idfor)
```

This function creates a database for each landscape, but with all pairs within landscape.

**Regression models**

* Jaccard Estimator

```{r}
jm.modelfor <- lm((1 - m.for[, 4]) ~ m.for[, 6])
jm.modelmix <- lm((1 - m.mix[, 4]) ~ m.mix[, 6])
jm.modelmea <- lm((1 - m.mea[, 4]) ~ m.mea[, 6])
```

* Sorensen Estimator

```{r}
sm.modelfor <- lm((1 - m.for[, 5]) ~ m.fordata[, 6])
sm.modelmix <- lm((1 - m.mix[, 5]) ~ m.mixdata[, 6])
sm.modelmea <- lm((1 - m.mea[, 5]) ~ m.meadata[, 6])
```

1. Forest

```{r forestlandscape1, fig.width = 12, fig.height = 4, echo = FALSE}
par(mfrow = c(1, 2))
plot(m.for[, 6], 1 - m.for[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(jm.modelfor)[[1]], b = coef(jm.modelfor)[[2]], col = 2, lwd = 4.5)
plot(m.for[, 6], 1 - m.for[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Forest")
abline(a = coef(sm.modelfor)[[1]], b = coef(sm.modelfor)[[2]], col = 2, lwd = 4.5)
```

2. Shrub

```{r shrublandscape1, fig.width = 12, fig.height = 4, echo = FALSE}
par(mfrow=c(1, 2))
plot(m.mix[, 6], 1 - m.mix[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(jm.modelmix)[[1]], b = coef(jm.modelmix)[[2]], col = 2, lwd = 4.5)
plot(m.mix[, 6], 1 - m.mix[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Shrub")
abline(a = coef(sm.modelmix)[[1]], b = coef(sm.modelmix)[[2]], col = 2, lwd = 4.5)
```

3. Meadow

```{r meadowlandscape1, fig.width = 12, fig.height = 4, echo = FALSE}
par(mfrow=c(1, 2))
plot(m.mea[, 6], 1 - m.mea[, 4], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Agric")
abline(a = coef(jm.modelmea)[[1]], b = coef(jm.modelmea)[[2]], col = 2, lwd = 4.5)
plot(m.mea[, 6], 1 - m.mea[, 5], ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
     ylab = expression(~beta*"-diversity"), main = "Agric")
abline(a = coef(sm.modelmea)[[1]], b = coef(sm.modelmea)[[2]], col = 2, lwd = 4.5)
```

* Mean Dissimilarity for each scale

```{r}
plot.scale2 <- function(base, estimator = 0){
  #if estimator == 0: Jaccard, otherwise: Sorensen (default is Jaccard)
  area <- base[, 6]
  if(estimator) div <- base[, 5]
  else div <- base[, 4]
  plot(area, 1 - div, ylim = c(0, 1), xlim = c(0, 2000), xlab = "Geographic Distance (m)", 
       ylab = expression(~beta*"-diversity"))
  abline(v = c(115, 455), col = "gray", lwd = 1.5, lty = 2)
  lines(1:115, rep(1 - mean(div[area <= 115]), 115), col = 2, lwd = 4.5)
  lines(116:445, rep(1 - mean(div[(area <= 445) & (area > 115)]), 330), col = 2, lwd = 4.5)
  lines(446:1810, rep(1 - mean(div[area > 445]), 1365), col = 2, lwd = 4.5)
}

```

1. Forest

```{r forestscale, fig.width = 12, fig.height = 6, echo = TRUE}
par(mfrow = c(1, 2))
plot.scale2(m.for)
plot.scale2(m.for, 1)
```

2. Shrub

```{r shrubscale, fig.width = 12, fig.height = 6, echo = FALSE}
par(mfrow = c(1, 2))
plot.scale2(m.mix)
plot.scale2(m.mix, 1)
```

3. Meadow

```{r meadowscale, fig.width = 12, fig.height = 6, echo = FALSE}
par(mfrow = c(1, 2))
plot.scale2(m.mea)
plot.scale2(m.mea, 1)
```

**Bootstrapping**

```{r, echo = FALSE}
interc.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[1, 1], base2[1, 1], base3[1, 1])
  l.ci <- c(base1[1, 2], base2[1, 2], base3[1, 2])
  s.ci <- c(base1[1, 3], base2[1, 3], base3[1, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim =c(0, 1), ylab = "Intercept", xlab = "", pch = "-", lwd = 2)
  #title("All Years - Jaccard Estimator", outer = TRUE, cex = 1.5)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

dissim.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[4, 1], base2[4, 1], base3[4, 1])
  l.ci <- c(base1[4, 2], base2[4, 2], base3[4, 2])
  s.ci <- c(base1[4, 3], base2[4, 3], base3[4, 3])
  plot(1:3, 1 - mean.ci, xaxt = "n", ylim =c(0, 1), ylab = expression(~beta*"-diversity"), xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
  segments(x0 = 1:3, y0 = 1 - l.ci, y1 = 1 - s.ci)
  points(1:3, 1 - l.ci, lwd = 1.5, pch = "-")
  points(1:3, 1 - s.ci, lwd = 1.5, pch = "-")
}

slope.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[2, 1], base2[2, 1], base3[2, 1])
  l.ci <- c(base1[2, 2], base2[2, 2], base3[2, 2])
  s.ci <- c(base1[2, 3], base2[2, 3], base3[2, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "Slope", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

rsquar.plot3 <- function(base1, base2, base3){
  mean.ci <- c(base1[3, 1], base2[3, 1], base3[3, 1])
  l.ci <- c(base1[3, 2], base2[3, 2], base3[3, 2])
  s.ci <- c(base1[3, 3], base2[3, 3], base3[3, 3])
  plot(1:3, mean.ci, xaxt = "n", ylim = c(min(l.ci), max(s.ci)), ylab = "R-Square", xlab = "", pch = "-", lwd = 2)
  axis(1, at = 1:3, labels = c("Forest", "Shrub", "Meadow"))
  segments(x0 = 1:3, y0 = l.ci, y1 = s.ci)
  points(1:3, l.ci, lwd = 1.5, pch = "-")
  points(1:3, s.ci, lwd = 1.5, pch = "-")
}

# Table
boot.table2 <- function(base1, base2, base3, index = 1){
  #1: intercept; 2: slope; 3: r-square and 4: dissimilarity (default is intercept)
  mean.ci <- c(base1[index, 1], base2[index, 1], base3[index, 1])
  lower.ci <- c(base1[index, 2], base2[index, 2], base3[index, 2])
  upper.ci <- c(base1[index, 3], base2[index, 3], base3[index, 3])
  xt <- cbind(mean.ci, lower.ci, upper.ci)
  if(index == 4) xt <- 1 - xt
  rownames(xt) <- c("Forest", "Shrub", "Meadow")
  xt
}
```

```{r}
# function to obtain regression weights 
bs.jac <- function(formula, data, ind){
  d <- data[ind,] # allows boot to select sample
  fit <- lm(formula, data = d)
  return(c(coef(fit), summary(fit)$r.square, mean(d[, 4]))) 
} 

bs.sor <- function(formula, data, ind){
  d <- data[ind,] # allows boot to select sample
  fit <- lm(formula, data = d)
  return(c(coef(fit), summary(fit)$r.square, mean(d[, 5]))) 
} 
```

```{r, echo = FALSE}
ci.boot <- function(base){
  temp1 <- boot.ci(base, type="bca", index= 1) # intercept 
  temp2 <- boot.ci(base, type="bca", index = 2) # slope
  temp3 <- boot.ci(base, type="bca", index = 3) # r.square
  temp4 <- boot.ci(base, type="bca", index = 4) # mean
  base.ci <- rbind(cbind(temp1$t0, temp1$bca[4], temp1$bca[5]), cbind(temp2$t0, temp2$bca[4], 
  temp2$bca[5]), cbind(temp3$t0, temp3$bca[4], temp3$bca[5]), cbind(temp4$t0, temp4$bca[4], temp4$bca[5]))
  base.ci
}
```

**Within landscape**

```{r}
# bootstrapping with 2000 replications
jforres <- boot(data = as.data.frame(m.fordata), statistic = bs.jac, R = 2000, 
                formula = (1 - Jabd) ~ ipcc)
sforres <- boot(data = as.data.frame(m.fordata), statistic = bs.sor, R = 2000, 
                formula = (1 - Labd) ~ ipcc)
jmixres <- boot(data = as.data.frame(m.mixdata), statistic = bs.jac, R = 2000, 
                formula = (1 - Jabd) ~ ipcc)
smixres <- boot(data = as.data.frame(m.mixdata), statistic = bs.sor, R = 2000, 
                formula = (1 - Labd) ~ ipcc)

jmeares <- boot(data = as.data.frame(m.meadata), statistic = bs.jac, R = 2000, 
                formula = (1 - Jabd) ~ ipcc)
smeares <- boot(data = as.data.frame(m.meadata), statistic = bs.sor, R = 2000, 
                formula = (1 - Labd) ~ ipcc)
```

**Confidence Interval**

* Bootstrap 95% CI for regression coefficients

*Jaccard*

```{r}
jforres.ci <- ci.boot(jforres)
jmixres.ci <- ci.boot(jmixres)
jmeares.ci <- ci.boot(jmeares)
```

*Sorensen*

```{r}
jforres.ci <- ci.boot(jforres)
jmixres.ci <- ci.boot(jmixres)
jmeares.ci <- ci.boot(jmeares)
```

**Results**

* Intercept

```{r intercept_meth1, fig.width = 12, fig.height = 4}
par(mfrow = c(1, 2))
interc.plot3(jforres.ci, jmixres.ci, jmeares.ci)
title("Jaccard", cex = 1.5)
interc.plot3(sforres.ci, smixres.ci, smeares.ci)
title("Sorensen", cex = 1.5)
```

* Dissimilarity

```{r dissim_meth1, fig.width = 12, fig.height = 4}
par(mfrow = c(1, 2))
dissim.plot3(jforres.ci, jmixres.ci, jmeares.ci)
title("Jaccard", cex = 1.5)
dissim.plot3(sforres.ci, smixres.ci, smeares.ci)
title("Sorensen", cex = 1.5)
```

* Slope

```{r slope_meth1, fig.width = 12, fig.height = 4}
par(mfrow = c(1, 2))
slope.plot3(jforres.ci, jmixres.ci, jmeares.ci)
title("Jaccard", cex = 1.5)
slope.plot3(sforres.ci, smixres.ci, smeares.ci)
title("Sorensen", cex = 1.5)
```

* R-Square
```{r r-squar_meth1, fig.width = 12, fig.height = 4}
par(mfrow = c(1, 2))
rsquar.plot3(jforres.ci, jmixres.ci, jmeares.ci)
title("Jaccard", cex = 1.5)
rsquar.plot3(sforres.ci, smixres.ci, smeares.ci)
title("Sorensen", cex = 1.5)
```

# Tables

*Jaccard*

```{r, echo = TRUE, results = 'asis'}
print(xtable(boot.table2(jforres.ci, jmixres.ci, jmeares.ci), 
             digits = 4, caption = "Intercept"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(jforres.ci, jmixres.ci, jmeares.ci, 4), 
             digits = 4, caption = "Dissimilarity"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(jforres.ci, jmixres.ci, jmeares.ci, 2), 
             digits = 6, caption = "Slope"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(jforres.ci, jmixres.ci, jmeares.ci, 3), 
             digits = 4, caption = "R-square"), type = "latex", comment = FALSE)
```

*Sorensen*

```{r, echo = TRUE, results = 'asis'}
print(xtable(boot.table2(sforres.ci, smixres.ci, smeares.ci), 
             digits = 4, caption = "Intercept"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(sforres.ci, smixres.ci, smeares.ci, 4), 
             digits = 4, caption = "Dissimilarity"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(sforres.ci, smixres.ci, smeares.ci, 2), 
             digits = 6, caption = "Slope"), type = "latex", comment = FALSE)
```

```{r, echo = FALSE, results = 'asis'}
print(xtable(boot.table2(sforres.ci, smixres.ci, smeares.ci, 3), 
             digits = 4, caption = "R-square"), type = "latex", comment = FALSE)
```

